Uncovering underlying musical content in the temporal domain \\ \small Leveraging deep learning, inductive bias, and aural music skills to learn embedding spaces from raw waveforms with applications to MIR downstream tasks

### 2023-04-19 introduction/Subsections/Assumptions.tex
Updates from Overleaf

Although a waveform might have limited sheet music representations that accurately encapsulate its musical components, a single sheet music composition can be performed infinitely using various instruments, voices, tempos, and interpretations. The distinct tonal quality of a waveform is significantly influenced by the specific instrument or production technology employed in its creation, complicating the transcription of its sonic properties into precise sheet music notation.

@@

\begin{figure}[h]
\includegraphics[clip,width=\columnwidth]{figures/images/sheet1.png}% 
\caption{\small{XXXX}}
\label{fig: Sheet music aug 1}
\end{figure}

\begin{figure}[h]
\includegraphics[clip,width=\columnwidth]{figures/images/sheet2.png}% 
\caption{\small{XXXX}}
\label{fig: Sheet music aug 2}
\end{figure}

\begin{figure}[h]
\includegraphics[clip,width=\columnwidth]{figures/images/sheet3.png}% 
\caption{\small{XXXX}}
\label{fig: Sheet music aug 3}
\end{figure}

\begin{figure}[h]
\includegraphics[clip,width=\columnwidth]{figures/images/sheet4.png}% 
\caption{\small{XXXX}}
\label{fig: Sheet music aug 4}
\end{figure}

>>>>

Although a waveform might have limited sheet music representations that accurately encapsulate its musical components, a single sheet music composition can be performed infinitely using various instruments, voices, tempos, and interpretations. The distinct tonal quality of a waveform is significantly influenced by the specific instrument timbre or production technology employed in its creation, complicating the transcription of its sonic properties into precise sheet music notation.

@@

### 2023-04-19 introduction/Subsections/Introduction.tex
Updates from Overleaf

Music is an essential part of human culture, history, and society. It has existed since ancient times and evolved, reflecting changes in our cultures, traditions, and beliefs. Despite its importance, the study of music has always been a challenging and complex task due to its subjective nature and the vast array of musical styles, genres, and cultures that exist worldwide.

Humanity has been studying music to understand its underlying structure for millennia. From the ancient Greeks to the early days, music has been a subject of fascination and inquiry. This rich music theory and analysis history provide a valuable foundation for guiding and evaluating Music Information Retrieval (MIR) algorithms and models.

We all humbly seek to unlock the secrets of music's complex and multifaceted nature.

MIR is a research area that has emerged in the last decades as an interdisciplinary field combining engineering, musicology, and neuroscience. MIR aims to develop algorithms and techniques to automatically analyze, classify, and retrieve musical information from mainly audio signals. I believe that traditionally, MIR research has primarily concentrated on technical aspects, such as Digital Signal Processing (DSP) or pattern recognition. As a result, other relevant domains, including perception, cognition, music theory, aural skills, and musicology, along with its subfields, might have been overlooked.

It is worth mentioning that there has been a significant shift in this tendency on retrieval tasks in the symbolic and musicological domain, such as powerful open-source analysis frameworks \cite{ScottCuthbertChristopherArizaMusic21:Data}, MIDI to proper sheet music syntax \cite{Suzuki2021ScoreRepresentation}, projective orchestration \cite{Crestel2018AOrchestration}, or automatic lead sheet generation \cite{WeilAutomaticSignals} to name a few.

The reason behind this is non-other but the implementation complexity for such heuristics and abstract fields of study. Closing the gap between human perception, environmental and cultural factors, and computational solutions to mimic the formers is an already tackled topic \cite{Large1994ResonanceMeter}\cite{Mullensiefen2003MeasuringJudgments}\cite{Sears2014PerceivingCadence}\cite{Thaut2014HumanPatter}\cite{, yet remains a vast open challenge.

>>>>

Music, an essential component of human culture, history, and society, has existed since ancient times. It reflects the changes in our cultures, traditions, and beliefs as it evolves. Studying music, however, has always been a challenging and complex task due to its subjective nature and the sheer variety of musical styles, genres, and cultures that exist worldwide.

For millennia, people have sought to understand the underlying structure of music. Music has captivated and intrigued us from the ancient Greeks to the present day. This rich music theory and analysis history form a valuable foundation for guiding and evaluating Music Information Retrieval (MIR) algorithms and models.

Music Information Retrieval (MIR) has emerged over the last few decades as an interdisciplinary field that combines engineering, musicology, and neuroscience. It aims to develop algorithms and techniques for automatically analyzing, classifying, and retrieving musical information, primarily from audio signals. While MIR research has traditionally focused on technical aspects such as Digital Signal Processing (DSP) and pattern recognition, it may have overlooked other relevant domains, including perception, cognition, music theory, aural skills, and musicology, along with their subfields.

\subsubsection{Bridging the gap}

There has been a noticeable shift in this tendency in recent years, with a growing emphasis on retrieval tasks in the symbolic and musicological domain. Several powerful open-source analysis frameworks have emerged for the symbolic domain \cite{ScottCuthbertChristopherArizaMusic21:Data}, as well as advancements in MIDI to human-readable sheet music syntax \cite{Suzuki2021ScoreRepresentation}, projective orchestration \cite{Crestel2018AOrchestration}, and automatic lead sheet generation \cite{WeilAutomaticSignals}, among others.

The driving force behind this shift might be the recognition of the complexity of implementing heuristics and abstract fields of study. Bridging the gap between human perception \cite{Large1994ResonanceMeter}\cite{Thaut2014HumanPatter}, environmental and cultural factors \cite{Sears2014PerceivingCadence}, and computational solutions that mimic these aspects \cite{Mullensiefen2003MeasuringJudgments} is a topic that has been previously explored \cite{Hernandez-Olivan2023SymbolicMethods}.

Still, it remains a vast and open challenge.

### 2023-04-19 introduction/Subsections/Motivation.tex
Updates from Overleaf

\section{Motivation}
As a music lover, professional musician, and connoisseur, I am interested in gaining a deeper understanding of the fundamental building of musical composition, the various techniques used to create musical works, and capturing underlying relationships among them. I am deeply interested in learning how to retrieve useful embedded information within music.

@@

I have consistently been inspired by musicians and researchers who strive to uncover musical ground truth within the existing tonal paradigm, such as Heinrich Schenker, or by challenging it, as exemplified by George Russell \cite{LydianRussell}. Both approaches aim to identify abstract concepts that reinforce or disrupt the tonal foundation. Their ultimate goal is to advance the tonal landscape, providing musicians with a dependable playground for growth, development, and further understanding tonal paradigms.

@@

\begin{figure}[ht]
\includegraphics[clip,width=\columnwidth]{figures/schenkerian analysis/SchubertOp4no3.png}% 
\caption{Small excerpt of \textit{Wandrers Nachtlied, Op. 4, D. 224} by Franz Schubert. We can see the passage's original score, the schenkerian unfolding of the melody, the chord degrees, and the tonal function.}
\label{fig:Wandrers Nachtlied, Op. 4, D. 224}
\end{figure}

>>>>

\section{Motivation}
In the context of this thesis, the research was conducted in collaboration with Epidemic Sound \cite{EpidemicSite}, a renowned organization in the music technology sector. Acquiring an in-depth understanding of music and its fundamental structures serves not only to satisfy intellectual curiosity but also to generate potential advancements and benefits for the technical products and services offered by the company.

As a music enthusiast, professional musician, and scholar, I am fervently dedicated to examining the foundational elements of musical composition, investigating the diverse techniques employed in crafting musical pieces, and discerning the intricate relationships among them.

This passion motivates my pursuit of knowledge on extracting valuable information embedded within music, which can contribute to developing more sophisticated and effective music-related technologies and solutions in the industrial landscape.

By championing exposure as the primary method of learning music, I underscore the importance of immersing oneself in many musical experiences to foster a holistic understanding of music as an art form. Individuals can cultivate well-rounded musical expertise by engaging with various styles, genres, techniques, and learning approaches, ultimately promoting creativity and experimentation in both personal and professional domains.

@@

I have consistently been inspired by musicians and researchers who strive to uncover musical ground truth within the existing tonal paradigm, such as Heinrich Schenker, or by challenging it, exemplified by George Russell \cite{LydianRussell}. Both approaches aim to identify abstract concepts that reinforce or disrupt the tonal foundation. Their ultimate goal is to advance the tonal landscape, providing musicians with a dependable playground for growth, development, and further understanding tonal paradigms.

@@

\begin{figure}[ht]
\includegraphics[clip,width=\columnwidth]{figures/schenkerian analysis/SchubertOp4no3.png}% 
\caption{Small excerpt of \textit{Wandrers Nachtlied, Op. 4, D. 224} by Franz Schubert. We can see the passage's original score, the schenkerian unfolding of the melody, the chord degrees analysis, as well as the the tonal function.}
\label{fig:Wandrers Nachtlied, Op. 4, D. 224}
\end{figure}
